\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2017-07-21 doc/USER_MANUAL/04_creating_databases.tex
better sentence for f0_for_PML in the users manual

will be used in the calculation of PML damping profiles; this should
be set to the same (or similar) dominant frequency as that of the
source that you will use in your simulation. If you plan to use a
Dirac source, then use the dominant frequency of the source wavelet

>>>>

will be used in the calculation of PML damping profiles;
\red{This should be set to the same (or similar) dominant frequency as that of the
source that you will use in your simulation. It is \textbf{VERY IMPORTANT} to do that, otherwise the PML 
absorbing conditions can become unstable.}
If you plan to use a Dirac source, then use the dominant frequency of the source wavelet
